% =====================================================================
%  Gregory Dean Foster, Jr. — Résumé
% ---------------------------------------------------------------------
%  One file, two halves:
%    1. PREAMBLE — layout, fonts, colors, and a handful of semantic
%       macros (\role, \client, \pastrole, \skillrow). Tune spacing
%       and colors here; never in the content.
%    2. CONTENT — reads top to bottom like the finished document.
%
%  Build:  pdflatex resume.tex   (TeX Live 2020 or newer)
% =====================================================================
\documentclass[letterpaper,10pt]{article}

% ---------------------------------------------------------------------
%  1. PREAMBLE
% ---------------------------------------------------------------------
\usepackage[letterpaper,margin=0.75in]{geometry} % page + margins
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% Classical serif when available; falls back to Computer Modern on
% minimal TeX installs (e.g. Nix texlive-medium) so the build never breaks.
\IfFileExists{ebgaramond.sty}{\usepackage{ebgaramond}}{}
\usepackage{microtype}      % better justification
\usepackage{enumitem}       % compact, controllable lists
\usepackage{titlesec}       % section title styling
\usepackage{tabularx}       % skills table
\usepackage{xcolor}
\usepackage[colorlinks=true, urlcolor=golddark, linkcolor=ink]{hyperref}

% ---- palette (matches the web version) ------------------------------
\definecolor{ink}{HTML}{201F1D}      % body text
\definecolor{muted}{HTML}{605D5D}    % dates, locations
\definecolor{gold}{HTML}{B68235}     % hairline rules, bullets
\definecolor{golddark}{HTML}{7D5411} % links (dark enough to read)

\pagestyle{empty}
\setlength{\parindent}{0pt}
\raggedbottom
\color{ink}

% ---- section titles: large serif over a thin gold rule --------------
\titleformat{\section}
  {\Large}{}{0em}{}
  [{\color{gold}\vspace{-6pt}\titlerule[0.6pt]}]
\titlespacing{\section}{0pt}{12pt}{8pt}

% ---- semantic macros -------------------------------------------------
% \role{Company}{Location}{Title}{Dates} — a job heading (two lines)
\newcommand{\role}[4]{%
  \par\vspace{8pt}%
  \textbf{\large #1} \hfill {\small\color{muted}#4}\\
  \textit{#3} \hfill {\small\color{muted}#2}\par\vspace{1pt}}

% clients — the bulleted list under a role
\newenvironment{clients}
  {\begin{itemize}[leftmargin=13pt, itemsep=3pt, topsep=3pt,
                   label=\textcolor{gold}{\textbullet}]}
  {\end{itemize}}

% \client{Name}{What you did}            — undated entry
% \datedclient{Name}{Dates}{What you did} — dated entry
\newcommand{\client}[2]{\item \textbf{#1} — #2}
\newcommand{\datedclient}[3]{\item \textbf{#1} {\small\color{muted}(#2)} — #3}

% \pastrole{Company}{Title}{Dates}{One-line summary} — earlier roles
\newcommand{\pastrole}[4]{%
  \item \textbf{#1}, \textit{#2} {\small\color{muted}(#3)} — #4}

% \skillrow{Category}{Items} — one row of the skills table
\newcommand{\skillrow}[2]{\textbf{#1} & #2 \\[3pt]}

% tiny helpers
\newcommand{\sep}{\;\textperiodcentered\;}

% ---------------------------------------------------------------------
%  2. CONTENT
% ---------------------------------------------------------------------
\begin{document}

% ---- header ----------------------------------------------------------
{\huge Gregory Dean Foster, Jr.}\\[5pt]
{\small\color{muted}\scshape Technology Director \sep{} Enterprise \& Platform Architect}\\[3pt]
{\small Asheville, NC
  \sep \href{mailto:brona90@gmail.com}{brona90@gmail.com}
  \sep +1~(504)~355-7726
  \sep \href{https://github.com/brona90}{github.com/brona90}}
\vspace{6pt}
{\color{gold}\hrule height 0.6pt}
\vspace{8pt}

% ---- summary ---------------------------------------------------------
Technology director with 20 years of writing software, grown from Java
developer to enterprise architect. I lead architecture practices, cloud
modernization, and reliability transformations for Fortune 500 clients ---
building the standards, communities, and platforms that outlast the
engagement. Still hands-on: Go, Python, Terraform, and Kubernetes across
AWS, Azure, and GCP.

% ---- experience ------------------------------------------------------
\section{Experience}

\role{Cognizant}{Asheville, NC}{Director \& Technical Principal}{Jul 2022 -- Present}
Engagement lead for enterprise architecture, cloud security, and
reliability transformation. Selected client work:
\begin{clients}
  \datedclient{Goldman Sachs}{2026 -- present}{Lead architect for a
    large-scale cloud migration: discovery, migration strategy, and
    platform reference architecture.}
  \datedclient{Advance Auto Parts}{2025 -- 2026}{Lead architect for a
    completed AWS-to-GCP modernization: discovery, migration strategy,
    statements of work, and a Terraform-based data \& analytics
    reference architecture.}
  \datedclient{Truist}{2025}{Assessment principal for the platform
    organization: built the maturity-metrics methodology and
    ways-of-working framework; delivered the executive readout and
    recommendations.}
  \datedclient{Freddie Mac}{2025}{Led an SRE transformation assessment:
    reliability maturity evaluation, an automation roadmap for
    environment support, and executive materials later shared as an
    internal case study.}
  \datedclient{Elevance Health}{2023 -- 2025}{Established the
    security-architecture review process for cloud and platform
    modernization programs; personally conducted hundreds of
    architecture and security assessments.}
  \datedclient{AbbVie}{2022 -- 2023}{Stood up an enterprise-architecture
    practice for the OUS organization: ADR and ARB processes, a
    reference architecture built on volatility-based decomposition, an
    architecture community of practice, and weekly training
    publications.}
  \client{Cognizant internal}{Founded the consulting org's Security
    Community of Practice; co-led Cloudboost, a Go service provisioning
    guard-railed cloud accounts across all three major CSPs (EKS, Helm,
    Terraform, GitHub Actions).}
\end{clients}

\role{Nexient}{Asheville, NC}{Delivery Director, DevOps}{Aug 2021 -- May 2022}
\begin{clients}
  \client{GIA}{Delivered the reference architecture (volatility-based
    decomposition) for the Beacon lab-operations platform plus its
    DevSecOps runway --- GitHub Actions to AWS with templated Terraform
    modules --- and multi-region HA guidance.}
  \client{Fidelity}{Led a junior team through an on-prem Rancher-to-AKS
    migration: Helm charts, Jenkinsfiles, and centralized Datadog
    observability, documented end to end as client-ready process flows.}
  \client{Wesco \& bench}{Authored an evolutionary-database-design
    reference enabling dark deployments, feature toggles, and canary
    releases; trained bench consultants on Azure DevOps, Jenkins, and
    containerization.}
\end{clients}

\role{Contino}{New Orleans, LA}{Lead DevOps Consultant}{Oct 2020 -- Aug 2021}
\begin{clients}
  \client{Discover}{Designed and taught engineering dojos ---
    accelerated, hands-on classes in TDD, BDD, contract testing,
    vertical slicing, value-stream mapping, and CI/CD.}
  \client{The Hartford}{Designed and built private AWS-to-Snowflake
    connectivity for the data-science org in CloudFormation, with live
    milestone demos and best-practice training.}
\end{clients}

\role{DXC Technology}{New Orleans, LA}{Senior DevOps Engineer}{Oct 2018 -- Jun 2020}
\begin{clients}
  \client{Platform DXC}{Built the enterprise Kubernetes platform:
    standardized builds, Jenkins CI, Vault secrets management,
    Helm-charted tooling, custom resource definitions in Python, and a
    serverless API layer via Kubeless.}
  \client{Domain Task Orchestrator}{Designed the DAG-based orchestration
    service that let platform tools talk to one another, replacing
    incomplete legacy solutions; integrated it into the platform
    offering.}
  \client{Mentorship}{Ran ongoing training for junior teams: git,
    Python, Kubernetes, Docker, API design, and design patterns.}
\end{clients}

\role{Baker Hughes}{New Orleans, LA}{Staff Build \& Release Engineer}{Dec 2016 -- Oct 2018}
\begin{clients}
  \client{Platform Operations Advisor}{Owned build and release for a
    Predix industrial-IoT platform: Jenkins CI, a fully containerized
    stack, git-flow change management, semantic versioning, and
    automated Predix deployments --- coordinating every build engineer
    on the project.}
  \client{Digital Pipeline \sep{} Reliance}{Built CI infrastructure and
    Jenkins Job-DSL automation for two GIS monitoring products;
    containerized development environments and rewrote legacy build
    scripts to standard.}
\end{clients}

% ---- earlier experience ----------------------------------------------
\section{Earlier Experience}
\begin{clients}
  \pastrole{GE Digital}{Senior Software Engineer}{2016}{Selenium/jBehave
    test suite, jHipster adoption, legacy refactoring, SOLID mentoring.}
  \pastrole{GE Oil \& Gas}{Senior DevOps Engineer}{2015 -- 2016}{CI via
    shared Jenkins; Chef and Test Kitchen infrastructure for AWS;
    migration to scripted deployments.}
  \pastrole{GE Capital}{Senior Java Developer}{2012 -- 2015}{STIG-based
    SecureOS Chef solution; contract-first ESB middleware for online
    banking.}
  \pastrole{Applied Enterprise Solutions}{Java Developer}{2012}
    {WSDL-based services for a Naval inventory program.}
  \pastrole{U.S. Department of Energy}{Java Developer}{2011 -- 2012}
    {Java migration tooling moving millions of files into SharePoint.}
\end{clients}

% ---- skills ----------------------------------------------------------
\section{Skills}
\begin{tabularx}{\textwidth}{@{}p{1.55in}X@{}}
  \skillrow{Languages}{Go \sep Python \sep Java \sep Ruby \sep JavaScript
    \sep Bash \sep Lisp \sep \LaTeX}
  \skillrow{Cloud}{AWS \sep Azure \sep GCP \sep Cloud Foundry (Predix)}
  \skillrow{Platform \& delivery}{Kubernetes \sep Helm \sep Docker \sep
    Terraform \sep CloudFormation \sep Chef \sep Vault \sep Jenkins \sep
    GitHub Actions \sep Azure DevOps \sep Datadog}
  \skillrow{Practices}{Enterprise architecture (ADR \sep ARB) \sep
    Volatility-based decomposition \sep DevSecOps \sep SRE \sep TDD/BDD
    \sep CI/CD \sep Evolutionary database design}
\end{tabularx}

% ---- community -------------------------------------------------------
\section{Community}
\textbf{Operation Spark} \hfill {\small\color{muted}2019 -- 2021}\\
\textit{Created and taught the DevSecOps curriculum} \hfill {\small\color{muted}New Orleans, LA}

\end{document}
